Stack Safety is a Security Property

### 2021-04-16 tex/main.tex
7 + 8 unlocked

We propose a formal characterization
of stack safety, formulated with concepts from language-based security: a
combination of an integrity property (``the private
state in each caller's stack frame is held invariant by the callee'')
a confidentiality property (``the callee's behavior is insensitive to the
caller's private state''), and a well-bracketedness property (``each
callee returns control to its immediate caller'').
% These properties are sensible even in the presence of
% abnormal control flow.\apt{Is this important enough to mention here?}
% BCP: I think not in the abstract, but maybe in the intro.
% We further apply\apt{what does this mean? we didn't
%  invent it} a straightforward notion of
% ``well-bracketed control flow'' that restricts control flow to the
% typical pattern of matched calls and returns.
%
We use these properties to validate the stack-safety ``micro-policies''
proposed by~\citet{DBLP:conf/sp/RoesslerD18}.  Specifically, we check (with
property-based random testing) that Roessler and Dehon's ``eager''
micro-policy, which catches violations as early as possible, enforces a
simple ``stepwise'' variant of our properties and correctly detects several
broken variants, and that (a repaired version of) their more performant
``lazy'' micro-policy corresponds to a slightly weaker and more extensional
variant of our properties.
%
% \BCP{I still don't think the next sentence really nails it.  And (sigh) I am
%   still not really clear yet on whether our definition applies / might apply
%   to other enforcement mechanisms or not.  Saying that our attacker model is
%   stronger does not help---that should make it easier for us to describe
%   their protections, not harder.  So I don't understand what we're saying
%   here.}%
% %
% While we do not rule out other enforcement mechanisms, our
% definitions are strongly informed by micropolicy systems, especially
% our attacker model, which is stronger than other enforcement mechanisms
% can enable.

@@

%\bcp{Does use of unitialized variables lead to stack safety attacks?\apt{sure, via buffer overflow}}
%with the notion usually being
%defined negatively: through examples of stack-based exploits
%\rb{usually though not always; as noted below there are other
%  approaches}\bcp{Yes, we have to be very careful about this}.
%\leo{Examples at a high level}: such as -- does not overwrite return addresses, or ...
The most abstract characterization stack safety that we are aware of is
recent work by \citet{Skorstengaard+19b,Skorstengaard+19}, which defines stack safety as the conjunction of two
properties:
{\em local state encapsulation (LSE)} and {\em well-bracketed control flow (WBCF)}.
Informally, LSE says that the contents of
a caller's stack frame are not read and written while its callees (and their callees, etc.) are
executing, and WBCF says that callees always
return to the point just after their call (if they return at all).
Skorstengaard et al.{} formalize these properties by defining an idealized
machine in which they hold {\em by construction};
they then show that an enforcement
mechanism (in their case, hardware capabilities) guarantees stack safety, by
proving that an ordinary machine with enforcement simulates the idealized
machine.
%an enforcement mechanism (in their case, hardware
%capabilities)
%can then be shown to guarantee stack safety by exhibiting a fully abstract
%embedding function
%from the idealized machine to an ordinary machine equipped with this
%enforcement mechanism.  \bcp{Many OOPSLA readers/reviewers will not
%  understand that sentence.}
%%
%% While this work represents an important step in the right direction, we believe
%% there is still room to craft an operational characterization
%% of stack safety. \apt{Perhaps our rhetoric should be more micro-policy-specific here?}
%% In other words, we seek formal criteria that can be applied
%% to a mechanism for protecting stack-based low-level programs to judge
%% whether or not it actually ``guarantees stack safety.''
%% \rb{The remainder of this paragraph may be diving too quickly, would a reader be
%% confused by the references to these types of properties, yet to be introduced?}
%% We begin with a strong
%% local state encapsulation property that closely models the behavior of eager
%% micro-policies from \citet{DBLP:conf/sp/RoesslerD18}. This ``eager'' property
%% is too strong to characterize stack safety; reasonable enforcement mechanisms
%% exist that violate it. One such mechanism is a ``lazy'' tag policy, similar to
%% the one in \citet{DBLP:conf/sp/RoesslerD18}. We weaken local state encapsulation
%% to support this technique and argue that the new property, defined relative to an
%% arbitrary notion of observation. This property is still strong enough to prevent
%% the bad behaviors we associate with unsafe stack behavior, but weak enough that
%% other reasonable enforcement mechanisms can enforce it.

In the present work, we also aim to protect both stack data (like
LSE) and
control flow (like WBCF).  But our formulations of these properties are
somewhat different from those of Skorstengaard et al.  Rather than
defining stack safety implicitly,
as ``what a certain idealized machine does,'' our properties are
based on the technical framework of language-based
security\ifaftersubmission~\citep{??}\bcp{Maybe the Sabelfeld and Myers
  survey?}\fi.
Our core properties are \emph{stepwise stack integrity},
\emph{stepwise stack confidentiality}, and \emph{return to caller}.
% \BCP{On consideration
%   (especially in light of the weird ``C confuses A by returning directly to
%   A instead of returning to B so that B can finish up some stuff before
%   returning to A'' example\footnote{Actually, this example is not so weird.
%   If C, the attacker, can return a {\em result} directly to A, who is
%   expecting a result from B, then that is clearly bad!}), I
% agree now that we should discuss WBCF.  It should be kept as distinct as
% possible from the ``data safety'' part, since it is not really an
% information flow property.  But our treatment of it is interestingly
% different from StkTokens, because of our call annotations, and we should
% discuss that.}

\bcp{This para could be clearer.  (I can try to fix it later but I want to
  keep reading now...)}In formalizing these security concepts, we treat {\em each} caller as needing
protection from its immediate callees (which, in turn, need protection from
their immediate callees, etc.).
This approach is novel in that the
confidentiality\bcp{only?} property applies to many nested sub-traces within a single execution,
as opposed to traces of entire executions.
{\em Integrity} says that each caller's local data is protected from
modification by its callee(s),
motivated by the reasoning principle that local data persists across a
call.

For the confidentiality and integrity properties, we consider two variants.
The
{\em stepwise} variants formalize the intuition that a caller's
local data
is never modified during a call. {\em Confidentiality} says that a caller's
data is not leaked into its callee, and  that the callee cannot see uninitialized data.
As a reasoning principle, confidentiality guarantees that the callee's
behavior is determined only by a predictable interface (function arguments and
register contents) that does not include the caller's
local state or the uninitialized portion of the stack. This is formalized as a
{\em noninterference}-style property that, rather than comparing pairs of whole program traces,
compares a pair of sub-traces for each call, within other calls\bcp{?}. Once
again
{\em stepwise} describes the granularity of enforcement\bcp{?}: at every step of a call,
changes in the state are independent of the caller's data.

@@

The building blocks of the machine are {\em values} and {\em addresses}.
Both are drawn from some set of {\em words} \(\WORDS\), ranged over by \(\word\) and
\(\addr\), respectively.
%
Our machine states are composed of {\em components} \(\component\),
which are either addresses or register names (\(\reg\)) drawn from some set
\(\REGS\), which is assumed to include two special purpose registers: the
program counter {\PCname} and the stack pointer \(\SP\).
A {\em machine state} is a map from components to values.
%
    \[\component \in \COMPONENTS ::= \WORDS + \REGS \]
%
    \[\mach \in \MACHS ::= \COMPONENTS \rightarrow \WORDS\]
%
We have a total step function between machine states, written \(\mach \stepsto \mach'\).

% BCP: This will intentionally fail when someone adds the real intended
% definition of \WF!
\newcommand{\WF}{\mathit{WF}}

We now formalize the model of enforcement that we introduced in \Cref{sec:threat}.
A {\em policy} consists of a set of policy
states \(\pol \in \POLS\) and a policy step function \((\mach, \pol) \polstep \pol' \in
\MACHS \times \POLS \rightharpoonup \POLS\). This step function is partial;
it is undefined on input configurations that correspond to a policy fault. The policy
can see the machine state, but cannot modify it. The policy also provides a
well-formedness condition, \(\WF (\mpstatename \in \MACHS \times \POLS)\), describing
initial states that are properly configured.
%
A concrete policy based on \citet{DBLP:conf/sp/RoesslerD18} will be described in
\Cref{sec:enforcement}.

We lift the policy step function to operate on such pairs
by combining it with the regular step function for machine states.
%
\judgmenttwo{\(\mach \stepsto \mach'\)}{\((\mach, \pol)
               \polstep \pol'\)}
            {\(\mpstate{\mach}{\pol} \stepstopol
               \mpstate{\mach'}{\pol'}\)}
%
Note that the base machine has a total step function, while the policy-enhanced machine
refines it to a partial function. The extra policy state never changes behavior,
but it can cause
premature termination, representing failstop behavior.

@@

Separate from the machine state, we will keep track of additional context
information representing the history of the run. This has no influence on execution, it merely
describes information relevant to the particular property. Different information is needed
for different versions of the model, so the definitions are parameterized
over an arbitrary set of context states, \(\CONTEXTS\), annotations \(\ANNS\),
an initial context state \(\context_0 \in \CONTEXTS\), and a context step function
\(\mach, \context \constep \context' \in \MACHS \times \CONTEXTS
\times \rightarrow \CONTEXTS\). We also assume the existence of a \emph{code map},
\(\codemap \in \WORDS \rightharpoonup \ANNS\)
that relates each code address to its annotation, if any.
We lift contexts into an MP trace in much the same way as we lifted policy states to get
a triple state \(\mpcstatename \in \MPCS = \MACHS \times \POLS \times
\CONTEXTS\).

\judgmenttwo{\(\mpstate{\mach}{\pol} \stepstopol \mpstate{\mach'}{\pol'}\)}
              {\(\mach, \context \constep \context'\)}
              {\(\mpcstate{\mach}{\pol}{\context} \stepstocon
                \mpcstate{\mach'}{\pol'}{\context'}\)}

\subsection{Machine Traces}
\label{sec:traces}

A {\em machine trace} is a nonempty, finite or infinite sequence of elements
of MPC-states, ranged over by \(\MPCT\) and \(\NPCT\).
We use juxtaposition of an element and a trace to represent ``cons.'' (\bcp{Ugh})

The ``trace-of'' operator, written \(\mpcstatename \hookrightarrow \MPCT\),
coinductively relates an initial state with the trace of states
produced by repeated application of \(\stepstocon\)

@@

We project out the machine state of an MPC-state with \(\pi_\mach\), the
policy state with \(\pi_\pol\), and the context with \(\pi_\context\).
We take the first element of a trace with \(\head(\MPCT)\), which is a total
function since traces are non-empty, and the final element (if one exists) with
\(\last(\MPCT)\), which is partial.

\paragraph*{Until}
The operation \(\PUT ~ f ~ \MPCT\) takes a trace \(\MPCT\)
and a predicate on states \(f ~ \mpcstate \in \MPCS\) and gives the prefix of
\(\MPCT\) ending with the first element on which \(f\) holds.

\begin{center}
  \begin{minipage}{.3\textwidth}
    \judgment{\(f ~ \mpcstatename\)}
             {\(\PUT ~ f ~ \mpcstatename\MPCT = \mpcstatename\)}
  \end{minipage}
%
  \begin{minipage}{.3\textwidth}
    \judgment{}
             {\(\PUT ~ f ~ \mpcstatename = \mpcstatename\)}
%
  \end{minipage}
  \begin{minipage}{.3\textwidth}
    \judgmenttwo{\(\neg f ~ \mpcstatename\)}{\(\PUT ~ f ~ \MPCT = \MPCT'\)}
                {\(\PUT ~ f ~ \mpcstatename\MPCT = \mpcstatename\MPCT'\)}
  \end{minipage}
\end{center}
%
If the resulting trace is a strict prefix of the parameter, then the
predicate must hold on its final element. If the predicate always holds, then
\(\PUT\) is the identity function.

We will frequently take a prefix of the trace from an initial state up
through the first state where some condition holds on the machine state.
This can easily be implemented using \(\PUT\), and we provide special notation
for convenience.
%
If \(f\) is a predicate on machine states, we define \(\mpcstatename
\hookrightarrow \MPCT | f\) (read ``\(\MPCT\) is the prefix of
running \(\mpcstatename\) up to \(f\)''):
%
\begin{center}
\judgmenttwo{\(\mpcstatename \hookrightarrow \MPCT'\)}
            {\(\PUT ~ f ~ \mpcstatename ~ \MPCT' = \MPCT\)}
            {\(\mpcstatename \hookrightarrow \MPCT | f\)}
\end{center}

@@

individual calls from a trace by taking subtraces in which the stack is
at or below a given depth. If \(f\) is still a predicate on states, then
we define \(\mpcstatename \hookrightarrow \MPCT \langle f \rangle\), pronounced
``\(\mpcstatename\) segmented by \(f\) yields a sub-trace \(\MPCT\).''

\begin{center}
  \judgmenttwo[Now]
              {\(f ~ \mpcstatename\)}
              {\(\mpcstatename \hookrightarrow \MPCT | \neg f\)}
              {\(\mpcstatename \hookrightarrow \MPCT \langle f \rangle\)}
%
  \judgmentthree[Skip]
                {\(f ~ \mpcstatename\)}
                {\(\mpcstatename \hookrightarrow \MPCT | \neg f\)}
                {\(\last(\MPCT) \hookrightarrow \MPCT' \langle f \rangle\)}
                {\(\mpcstatename \hookrightarrow \MPCT' \langle f \rangle\)}
%
  \judgmentthree[Search]
                {\(\neg f ~ \mpcstatename\)}
                {\(\mpcstatename \hookrightarrow \MPCT | f\)}
                {\(\last(\MPCT) \hookrightarrow \MPCT' \langle f \rangle\)}
                {\(\mpcstatename \hookrightarrow \MPCT' \langle f \rangle\)}
\end{center}

@@

We often want to quantify over all traces from any initial state so that our
properties apply to the system as a whole. We say that a state \(\mpcstatename'\)
is {\em reachable} if for some initial state \(\mpcstatename = \mach,\pol,\context_0\)
where \(\WF ~ \mach,\pol\), \(\mpcstatename \hookrightarrow \MPCT\)
and \(\MPCT\) contains \(\mpcstatename'\). A {\it reachable segment} \(\MPCT \langle f \rangle\) is a subtrace
such that from some similarly well-formed initial state \(\mpcstatename\),
\(\mpcstatename \hookrightarrow \MPCT \langle f \rangle\).

@@

\definition For any depth \(\depth\), define \(f_\depth ~ \mach ~ (\_, \rts)\) to be
\(|\rts| \geq \depth\). Then each reachable segment \(\MPCT \langle f_\depth \rangle\)
corresponds to a trace of a function from its call to its return.
Given such a segment \(S\), let \(\mach,\_,(\domMap,\_)\)  = \(\head(S)\) and let
\(\components\) be the set of components \(\component\) such that \(\domMap ~ \component = \outside\).
A system enjoys \emph{stepwise stack confidentiality} if, for all \(\MPCT\langle f_\depth\rangle\)
with associated \(\mach\) and \(\components\) as above, and
for all \(\nach\) such that \(\mach \approx_\components \nach\) and
 \(\nach \hookrightarrow \NPCT\),
 \(\MPCT\langle f_\depth\rangle \doteq \NPCT | \neg f_\depth \).\apt{I found the previous
   version hopelessly confusing, but I'm not at all sure that this one is right! SNA please check.}
 \sna{It's right, but I need to rethink how the M<f> notation works...}

@@

\definition Let \(\depth\) be any depth and \(f_\depth ~ \mach ~ (\_, \rts)\) hold for
\(|\rts| \geq \depth\). For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\rts)\). Let
\(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \unsealed\) or \(\passed{\depth,\depth'}\) where
\(\depth \leq |\rts| \leq \depth'\) .
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT | \neg f_\depth\). A system enjoys
{\em stepwise stack confidentiality with passing} if for all such \(\MPCT\) and \(\NPCT\),
\(\MPCT \doteq \NPCT\).

@@

\definition Let \(\stackid\) be a stack identifier, \(\depth\) be any depth, and
\(f_\depth ~ \mach ~ (\_, \rtm, \_, \stackid)\) hold for \(|\rtm ~ \stackid| \geq \depth\).
For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\rtm,\yts,\stackid)\). Let
\(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid}{\_}\).
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT | \neg f_\depth\). A system enjoys
{\em stepwise coroutine confidentiality} in the coroutine setting if for all
such \(\MPCT\) and \(\NPCT\), \(\MPCT \doteq \NPCT\).

@@

\subsection{A Conservative Tag Policy}
\label{sec:conservative}

\bcp{Is this the only subsection in this section?}

>>>>

We propose a formal characterization
of stack safety, phrased using concepts from language-based security: a
combination of an integrity property (``the private
state in each caller's stack frame is held invariant by the callee'')
and a confidentiality property (``the callee's behavior is insensitive to the
caller's private state'')\bcp{and something about WBCF...}.
% These properties are sensible even in the presence of
% abnormal control flow.\apt{Is this important enough to mention here?}
% BCP: I think not in the abstract, but maybe in the intro.
% We further apply\apt{what does this mean? we didn't
%  invent it} a straightforward notion of
% ``well-bracketed control flow'' that restricts control flow to the
% typical pattern of matched calls and returns.
%
We use our characterization to validate the stack-safety ``micro-policies''
proposed by~\citet{DBLP:conf/sp/RoesslerD18}.
Specifically, we use property-based random testing to check that Roessler
and Dehon's ``eager'' micro-policy, which catches violations as early as
possible, enforces a simple ``stepwise'' variant of our properties (and
detects several broken variants), and that a slightly repaired version of
their more performant ``lazy'' micro-policy corresponds to weaker and more
extensional variants of the properties.
%
% \BCP{I still don't think the next sentence really nails it.  And (sigh) I am
%   still not really clear yet on whether our definition applies / might apply
%   to other enforcement mechanisms or not.  Saying that our attacker model is
%   stronger does not help---that should make it easier for us to describe
%   their protections, not harder.  So I don't understand what we're saying
%   here.}%
% %
% While we do not rule out other enforcement mechanisms, our
% definitions are strongly informed by micropolicy systems, especially
% our attacker model, which is stronger than other enforcement mechanisms
% can enable.

@@

%\bcp{Does use of unitialized variables lead to stack safety attacks?\apt{sure, via buffer overflow}}
%with the notion usually being
%defined negatively: through examples of stack-based exploits
%\rb{usually though not always; as noted below there are other
%  approaches}\bcp{Yes, we have to be very careful about this}.
%\leo{Examples at a high level}: such as -- does not overwrite return addresses, or ...
The most abstract characterization stack safety that we are aware of is in
recent work by \citet{Skorstengaard+19}, which defines stack safety as the conjunction of two
properties:
{\em local state encapsulation (LSE)} and {\em well-bracketed control flow (WBCF)}.
Informally, LSE says that the contents of
a caller's stack frame are not read and written while its callees (and their callees, etc.) are
executing, and WBCF says that callees always
return to the point just after their call (if they return at all).
Skorstengaard et al.{} formalize these properties by defining an idealized
machine in which they hold {\em by construction};
they then show that an enforcement
mechanism (in their case, hardware capabilities) guarantees stack safety, by
proving that an ordinary machine with enforcement can simulate the idealized machine.
%an enforcement mechanism (in their case, hardware
%capabilities)
%can then be shown to guarantee stack safety by exhibiting a fully abstract
%embedding function
%from the idealized machine to an ordinary machine equipped with this
%enforcement mechanism.  \bcp{Many OOPSLA readers/reviewers will not
%  understand that sentence.}
%%
%% While this work represents an important step in the right direction, we believe
%% there is still room to craft an operational characterization
%% of stack safety. \apt{Perhaps our rhetoric should be more micro-policy-specific here?}
%% In other words, we seek formal criteria that can be applied
%% to a mechanism for protecting stack-based low-level programs to judge
%% whether or not it actually ``guarantees stack safety.''
%% \rb{The remainder of this paragraph may be diving too quickly, would a reader be
%% confused by the references to these types of properties, yet to be introduced?}
%% We begin with a strong
%% local state encapsulation property that closely models the behavior of eager
%% micro-policies from \citet{DBLP:conf/sp/RoesslerD18}. This ``eager'' property
%% is too strong to characterize stack safety; reasonable enforcement mechanisms
%% exist that violate it. One such mechanism is a ``lazy'' tag policy, similar to
%% the one in \citet{DBLP:conf/sp/RoesslerD18}. We weaken local state encapsulation
%% to support this technique and argue that the new property, defined relative to an
%% arbitrary notion of observation. This property is still strong enough to prevent
%% the bad behaviors we associate with unsafe stack behavior, but weak enough that
%% other reasonable enforcement mechanisms can enforce it.

In the present work, we also distinguish between protecting stack data (like
LSE) and
control flow (like WBCF).  But our formulations of both properties are
somewhat different from those of Skorstengaard et al.  Rather than
defining stack safety implicitly,
as ``what a certain idealized machine does,'' we formalize explicit properties
based on the technical framework of language-based
security\ifaftersubmission~\citep{??}\bcp{Maybe the Sabelfeld and Myers
  survey?}\fi.
Our core properties are \emph{stepwise stack integrity} and
\emph{stepwise stack confidentiality}.  WBCF is a desireable property, but
we can express safety in an information-flow sense without reference to it,
even safety from attacks that hijack control flow.  \BCP{On consideration
  (especially in light of the weird ``C confuses A by returning directly to
  A instead of returning to B so that B can finish up some stuff before
  returning to A'' example\footnote{Actually, this example is not so weird.
  If C, the attacker, can return a {\em result} directly to A, who is
  expecting a result from B, then that is clearly bad!}), I
agree now that we should discuss WBCF.  It should be kept as distinct as
possible from the ``data safety'' part, since it is not really an
information flow property.  But our treatment of it is interestingly
different from StkTokens, because of our call annotations, and we should
discuss that.}

\bcp{This para could be clearer.  (I can try to fix it later but I want to
  keep reading now...)}In formalizing these security concepts, we treat {\em each} caller as needing
protection from its callee (which, in turn, needs protection from its
callee, etc.).
This is novel in that the
confidentiality property applies to many nested sub-traces within a single execution,
as opposed to traces of entire executions.
{\em Integrity} says that each caller's local data is protected from
modification by its callee(s),
motivated by the reasoning principle that local data persists across a call. Its
{\em stepwise} interpretation\bcp{We're introducing ``stepwise'' in a pretty
abrupt way---potentially confusing.} formalizes this very naturally: a caller's local data
is never modified during a call. {\em Confidentiality} says that a caller's
data is not leaked into its callee, and  that the callee cannot see uninitialized data.
As a reasoning principle, confidentiality guarantees that the callee's
behavior is determined only by a predictable interface (function arguments and
register contents) that does not include the caller's
local state or the uninitialized portion of the stack. This is formalized as a
{\em noninterference}-style property that, rather than comparing pairs of whole program traces,
compares a pair of sub-traces for each call, within other calls\bcp{?}. Once
again
{\em stepwise} describes the granularity of enforcement\bcp{?}: at every step of a call,
changes in the state are independent of the caller's data.

@@

The basic building blocks of the machine are {\em values} and {\em addresses}.
Both are drawn from some set of {\em words} \(\WORDS\), ranged over by \(\word\).
%
Our machine states are composed of {\em components} \(\component\),
which are either memory addresses (words) or register names (\(\reg\)) drawn from some set
\(\REGS\), which is assumed to include two special purpose registers: the
program counter {\PCname} and the stack pointer \(\SP\).
%
    \[\component \in \COMPONENTS ::= \WORDS + \REGS \]
%
A {\em machine state} is a map from components to values:
%
\[\mach \in \MACHS ::= \COMPONENTS \rightarrow \WORDS\]
%
We have a total step function between machine states, written \(\mach \stepsto \mach'\).
\apt{But just below we write $\mach \stepstoobs \mach'$. Which is it?}
\apt{Say something about initial machine state?}

\subsection{Policies}

We now formalize the model of enforcement that we introduced in \Cref{sec:threat}.
A {\em policy} consists of a set of policy
states \(\pol \in \POLS\) and a policy step function \((\mach, \pol) \polstep \pol' \in
\MACHS \times \POLS \rightharpoonup \POLS\). This step function is partial;
it is undefined on input configurations that correspond to a policy fault. The policy
can see the machine state, but cannot modify it. We assume that the
compiler\bcp{why?} provides an initial policy state \(\pol_0\) to accompany the initial machine state.\apt{see comment above}
%
A concrete policy based on \citet{DBLP:conf/sp/RoesslerD18} will be described in
\Cref{sec:enforcement}.

We write $\MPS$ for the set of all pairs of machine states and policy
states.
%
\[\mpstatename \in \MPS = \MACHS \times \POLS\]
%
We lift the policy step function to operate on such pairs
by combining it with the regular step function for machine states.

\judgmenttwo{\(\mach \stepstoobs \mach'\)}{\((\mach, \pol)
               \polstep \pol'\)}
            {\(\mpstate{\mach}{\pol} \stepstopol
               \mpstate{\mach'}{\pol'}\)}

\noindent
This combined step function is also partial, and traces of the machine-with-policy
will be finite iff a policy fault occurs.

@@

Separate from the machine state, our formal properties will keep track of additional context
information representing the history of the run. The following definitions are parameterized
over an arbitrary\bcp{why?} set of context states, \(\CONTEXTS\), annotations \(\ANNS\),
an initial context state \(\context_0 \in \CONTEXTS\), and a context step function
\(\mach, \context, \anns \constep \context' \in \MACHS \times \CONTEXTS
\times \powerset(\ANNS) \rightarrow \CONTEXTS\). We also assume a set of function identifiers
\(\FUNIDS\) and the existence of a \emph{code map} \(\codemap \in \WORDS \rightharpoonup \FUNIDS \times \powerset(\ANNS)\)
that relates each code address to its owning function and set of annotations.
We lift contexts into an MP trace in much the same way as we lifted policy states to get
a state type \(\mpcstatename \in \MPCS = \MACHS \times \POLS \times
\CONTEXTS\).  \bcp{I don't get the intuition for this whole para.}

\judgmentthree{\(\mpstate{\mach}{\pol} \stepstopol \mpstate{\mach'}{\pol'}\)}
              {\(\codemap ~ (\mach ~ \PCname) = \funid, \anns\)}
              {\(\mach, \context, \anns \constep \context'\)}
              {\(\mpcstate{\mach}{\pol}{\context} \stepstocon
                \mpcstate{\mach'}{\pol'}{\context'}\)}

\subsection{Traces}
\label{sec:traces}

A trace \(T \in \TRACE{\TRACEELEMS}\) is a nonempty, finite or infinite sequence of elements
of some type \(\TRACEELEMS\).  We will mostly be concerned with sequences of MPC-states,
called \emph{machine traces} and denoted \(\MPCT \in \TRACE{\MPCS}\). %, and of observations.

\paragraph*{Trace-Of}

The ``trace-of'' operator, written \(\mpcstatename \hookrightarrow \MPCT\),
coinductively relates an initial state with the trace of states
produced by repeated application of \(\stepstocon\), and potentially cut short by
the policy component. % The {\sc Default} rule applies only if the other does not.
(We use juxtaposition of an element and a trace to represent ``cons.''\bcp{Ugh})

@@

\paragraph*{Projections}

We project out the machine state of an MPC-state with \(\pi_\mach\), the
policy state with \(\pi_\pol\), and the context with \(\pi_\context\). We overload
these operators to project out of an machine-trace a trace of machine states,
policy states, and contexts, respectively.

\paragraph*{Head and Last}

We take the first element of a trace with \(\head(\Trace)\), which is a total
function since traces are non-empty, and the final element (if one exists) with
\(\last(\Trace)\), which is partial.

\paragraph*{Until}
The operation \(\PUT ~ f ~ \Trace\) takes a trace
\(\Trace \in \TRACE{\TRACEELEMS %\times \OBSS
}  \) and a predicate
on elements \(f \subset \TRACEELEMS\) and gives the prefix of
\(\Trace\) ending with the first element on which \(f\) holds.

\begin{center}
  \begin{minipage}{.3\textwidth}
    \judgment{\(f ~ \traceelem\)}
             {\(\PUT ~ f ~ \traceelem\Trace = \traceelem\)}
  \end{minipage}
%
  \begin{minipage}{.3\textwidth}
    \judgment{}
             {\(\PUT ~ f ~ \traceelem = \traceelem\)}
%
  \end{minipage}
  \begin{minipage}{.3\textwidth}
    \judgmenttwo{\(\neg f ~ \traceelem\)}{\(\PUT ~ f ~ \Trace = \Trace'\)}
                {\(\PUT ~ f ~ \traceelem\Trace = \traceelem\Trace'\)}
  \end{minipage}
\end{center}
%
\apt{If we are writing \(f \subset \TRACEELEMS\), perhaps we should also
  be writing \(a \in f\), etc.  rather than \(f a\), etc.?}
If the resulting trace is a strict prefix of the parameter, then the
predicate must hold on its final element. If the predicate always holds, then
\(\PUT\) is the identity function.

% The {\it join} operation, written \(T_1 \cdot T_2\) is the reverse of
%$\mathit{split}$: it takes two traces and links them by replacing the
%last element of the first (if it has one) with the first element of
%the second

%\judgment{} {\(t \cdot T = T\)}
%\judgment{\(T_1 \cdot T_2 = T\)}{\(tT_1 \cdot T_2 = tT\)}
%\leo{Lemma/theorem: split/join = id?}
%\leo{TODO: FORMATTING: Remove force line break/par at end of judgments}

We will frequently take a prefix of the trace from an initial state up
through the first state where some condition holds on the machine state.
This can easily be implemented using \(\PUT\), and we provide special notation
for convenience.
%
If \(f\) is a predicate on machine states, we define \(\mpcstatename
\hookrightarrow \MPCT | f\) (read ``\(\MPCT\) is the prefix of
running \(\mpcstatename\) up to \(f\)'') and similarly\apt{??} for traces with policies:

\begin{center}
\judgmenttwo{\(\mpcstatename \hookrightarrow \MPCT'\)}
            {\(\PUT ~ f ~ \mpcstatename ~ \MPCT' = \MPCT\)}
            {\(\mpcstatename \hookrightarrow \MPCT | f\)}
\end{center}

@@

In particular, we wish to formulate properties about consecutive sub-traces
in which the context obeys a given predicate. This will commonly be used to extract
individual calls from a trace by taking sub-traces in which the stack is
at or below a given depth\bcp{needed??}. If \(f \subseteq \MACHS \times \CONTEXTS\), then
we define \(\mpcstatename \hookrightarrow \MPCT \langle f \rangle\), pronounced
``\(\mpcstatename\) segmented by \(f\) yields a sub-trace \(\MPCT\).''

\begin{center}
  \judgmenttwo[Now]
              {\(f ~ \mach ~ \context\)}
              {\(\mach,\pol,\context \hookrightarrow \MPCT | \neg f\)}
              {\(\mach,\pol,\context \hookrightarrow \MPCT \langle f \rangle\)}
%
  \judgmentthree[Skip]
                {\(f ~ \mach ~ \context\)}
                {\(\mach,\pol,\context \hookrightarrow \MPCT | \neg f\)}
                {\(\last(\MPCT) \hookrightarrow \MPCT' \langle f \rangle\)}
                {\(\mach,\pol,\context \hookrightarrow \MPCT' \langle f \rangle\)}
%
  \judgmentthree[Search]
                {\(\neg f ~ \mach ~ \context\)}
                {\(\mach,\pol,\context \hookrightarrow \MPCT | f\)}
                {\(\last(\MPCT) \hookrightarrow \MPCT' \langle f \rangle\)}
                {\(\mach,\pol,\context \hookrightarrow \MPCT' \langle f \rangle\)}
\end{center}

@@

We often want to quantify over all traces from any initial state so that our
properties apply to the system as a whole. We say that a state \(\mpcstatename'\)
is {\em reachable} if for some initial state \(\mpcstatename\), \(\mpcstatename \hookrightarrow \MPCT\)
and \(\MPCT\) contains \(\mpcstatename'\). A {\it reachable segment} \(\MPCT \langle f \rangle\) is a sub-trace
such that from some initial state \(\mpcstatename\), \(\mpcstatename \hookrightarrow \MPCT \langle f \rangle\).
\apt{Unclear how there can be multiple initial states.}

@@

\definition For any depth \(\depth\), define \(f_\depth ~ \mach ~ (\_, \rts)\) to be
\(|\rts| \geq \depth\). Then each reachable segment \(\MPCT \langle f_\depth \rangle\)
corresponds to a trace of a function from its call to its return.
Given such a segment \(S\), let \(\mach,\_,(\domMap,\_)\)  = \(\head(S)\) and let
\(\components\) be the set of components \(\component\) such that \(\domMap ~ \component = \outside\).
A system enjoys \emph{stepwise stack confidentiality} if, for all \(\MPCT\langle f_\depth\rangle\)
with associated \(m\) and \(\components\) as above, and
for all \(\nach\) such that \(\mach \approx_\components \nach\) and
 \(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\),
 \(\MPCT\langle f_\depth\rangle \doteq \NPCT\langle f_\depth\rangle \).\apt{I found the previous
   version hopelessly confusing, but I'm not at all sure that this one is right! SNA please check.}
%% \definition Let \(\depth\) be any depth and \(f_\depth ~ \mach ~ (\_, \rts)\) hold for
%% \(|\rts| \geq \depth\). For any reachable segment \(\MPCT \langle f_\depth \rangle\),
%% let \(\head(\MPCT) = \mach,\pol,(\domMap,\rts)\) and
%%  \(\components\) be the set of components \(\component\) such that \(\domMap ~ \component = \outside\).
%% \(\MPCT\) corresponds to the trace of a function from its call to its return.
%% Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
%% \(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\). A system enjoys
%% {\em stepwise stack confidentiality} if for all such \(\MPCT\) and \(\NPCT\),
%% \(\MPCT \doteq \NPCT\).

@@

\definition Let \(\depth\) be any depth and \(f_\depth ~ \mach ~ (\_, \rts)\) hold for
\(|\rts| \geq \depth\). For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\rts)\). Let
\(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \unsealed\) or \(\passed{\depth,\depth'}\) where
\(\depth \leq |\rts| \leq \depth'\) .
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\). A system enjoys
{\em stepwise stack confidentiality with passing} if for all such \(\MPCT\) and \(\NPCT\),
\(\MPCT \doteq \NPCT\).

@@

\definition Let \(\stackid\) be a stack identifier, \(\depth\) be any depth, and
\(f_\depth ~ \mach ~ (\_, \rtm, \_, \stackid)\) hold for \(|\rtm ~ \stackid| \geq \depth\).
For any reachable segment \(\MPCT \langle f_\depth \rangle\),
let \(\head(\MPCT) = \mach,\pol,(\domMap,\rtm,\yts,\stackid)\). Let
\(\components\) be the set of components \(\component\) such that
\(\domMap ~ \component = \instack{\stackid}{\_}\).
Then take any \(\nach\) such that \(\mach \approx_\components \nach\), and
\(\nach \hookrightarrow \NPCT\langle f_\depth \rangle\). A system enjoys
{\em stepwise coroutine confidentiality} in the coroutine setting if for all
such \(\MPCT\) and \(\NPCT\), \(\MPCT \doteq \NPCT\).

@@

%\paragraph{A Conservative Tag Policy}
%\label{sec:conservative}
